---
title: "Prevalence of Norovirus in Portuguese Production Areas"
author: "Luis Oliveira"
date: "13/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Norovirus
During the past 2 years, IPMA have been collecting oysters from the portguese production areas for Norovirus testing. The location of the points can be found in the map below

```{r datamimport, echo=FALSE, error=FALSE, warning=FALSE, include=FALSE}
library(data.table)
library(here)
library(magrittr)
library(knitr)
library(kableExtra)
library(leaflet)
library(ggplot2)
library(ggthemes)

# Reads the data
NoV <- fread(here("data", "production_areas.csv"))

# Modifies spatial data as numeric
NoV[, long:=as.numeric(gsub(",", ".", longitude))]
NoV[, lat:=as.numeric(gsub(",", ".", latitude))]
NoV[, c("longitude", "latitude"):=NULL]

# Aggregrates date columns for sample, arrival and analysis
NoV[, sampDate:=as.Date(with(NoV, paste(sampY, sampM, sampD, sep = "/")), "%Y/%m/%d")][
    , arrivalDate:=as.Date(with(NoV, paste(sampY, sampM, arrivalD, sep = "/")), "%Y/%m/%d")][
    , analysisDate:=as.Date(with(NoV, paste(analysisY, analysisM, analysisD, sep = "/")), "%Y/%m/%d")]
NoV[, f.analysisDate:=as.factor(analysisDate)]
```

# Introduction
During the past 2 years, IPMA have been collecting oysters from the portguese production areas for Norovirus testing. The location of the points can be found in the map below.

```{r myMap, echo=FALSE, error=FALSE, warning=FALSE}
# Creates a map with the dataset coordinates
myMap <- leaflet(NoV) %>% 
         addTiles() %>% 
         addMarkers(lng = ~long, lat = ~lat, clusterOptions = markerClusterOptions())
myMap
```

# Results
Norovirus were found during the winter months, in particular between november and february. The summary of the results are listed on the next table.
```{r summary, echo=FALSE, error=FALSE, warning=FALSE}
# Creates summary table
NoVSum <- NoV[, .(N = .N, Mean = mean(resVal, na.rm = TRUE), SD = sd(resVal, na.rm = TRUE)), by = .(f.analysisDate)]

# Creates a tidy version of the previous table
NoVSum %>%
kable(align = "lrrr", digits = c(0, 1, 1, 1)) %>%
kable_styling(bootstrap_options = "striped", font_size = 12)
```


Below there's 3 diffent representation of the results.

## Point graph
```{r pgraph, echo=FALSE, error=FALSE, warning=FALSE}
# Creates a point graph of the summary table
NoV %>%
ggplot(aes(f.analysisDate, resVal)) +
  geom_point() +
  scale_x_discrete(
    labels = c("nov-dez 16", "jan-fev 17", "mar-apr 17", "may-jun 17", "jul-aug 17", "sep-oct 17", "nov-dez 17", "jan-fev 18", "mar-apr 18", "may-jun 18", "jul-aug 18", "sep-oct 18")) +
  xlab("Months") +
  ylab("Genome copies per gram") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Box-plot graph
```{r bpgraph, echo=FALSE, error=FALSE, warning=FALSE}
# Creates a boxplot graph of the summary table
NoV %>%
ggplot(aes(f.analysisDate, resVal)) +
  geom_boxplot() +
  scale_x_discrete(
    labels = c("nov-dez 16", "jan-fev 17", "mar-apr 17", "may-jun 17", "jul-aug 17", "sep-oct 17", "nov-dez 17", "jan-fev 18", "mar-apr 18", "may-jun 18", "jul-aug 18", "sep-oct 18")) +
  xlab("Months") +
  ylab("Genome copies per gram") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Column graph
```{r cgraph, echo=FALSE, error=FALSE, warning=FALSE}
# Creates a column graph of the summary table
NoV %>%
ggplot(aes(f.analysisDate, resVal)) +
  geom_col() +
  scale_x_discrete(
    labels = c("nov-dez 16", "jan-fev 17", "mar-apr 17", "may-jun 17", "jul-aug 17", "sep-oct 17", "nov-dez 17", "jan-fev 18", "mar-apr 18", "may-jun 18", "jul-aug 18", "sep-oct 18")) +
  xlab("Months") +
  ylab("Genome copies per gram") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


